### 2019-07-30 reports/thesis/chapters/1_literatureReview.tex
Revise lit review

X-ray computed tomography (XCT) can be used as a non-destructive test for additive manufactured objects, this is the main theme of this thesis. Various reviews on additive manufacturing exist such as \cite{kruth1991material, kruth1998progress, pham1998comparison, gibson2010additive, wong2012review, ngo2018additive}. For XCT used in manufacturing, there are \cite{cantatore2011introduction, kruth2011computed, sun2012overview}. \cite{thompson2016x} reviewed the applications of XCT on AM.

@@

Loosely, AM involves solidifying material onto a moving platform so that the object is manufactured layer by layer. Typically this is a slow and expensive method compared to destructive methods such as drilling and cutting for example. However, this is not the full picture. The set up cost for AM is low, in particular destructive methods requires planning and setting up various apparatus before the manufacturing stage \citep{gibson2010additive}. This is why AM used to be called rapid prototyping \citep{kruth1991material}, it was suitable to manufacture bespoke items.

@@

Fused deposition modelling is another liquid based AM technology. A jetting head, or nozzle, deposit the molten material onto a platform or on top of the previous layer. The material is usually plastic in a form of a thin filament. It is heated to just above its melting points, typically \SI{1}{\degreeCelsius} \citep{crump1992apparatus}, so that it cools down within \SI{0.1}{\second} \citep{kruth1991material}. The platform moves, and controlled by a computer, in the $x-y$ axis, or left to right and front to back, to produce a layer. The jetting head can move in the $z$ axis, or up and down, to manufacture the next layer. In the original patent by \cite{crump1992apparatus}, the thickness can be as thin as 0.0001 inches (\SI{0.003}{\milli\metre}).

@@

The blueprint of the object to be manufactured is called a computer-aided design (CAD). For it to be processed by an AM apparatus, the CAD is converted to a STL file \citep{3d1989sterolithography, 3d2019what} which represent surfaces made up of a series of triangles, an example is shown in Figure \ref{fig:literature_stl}. STL stands for sterolithography but could also be called standard tessellation language \citep{wong2012review}. Some accuracy is lost here as the surface of the CAD is represented approximately by triangles \citep{gibson2010additive}. The STL file is then sliced into layers \citep{jamieson1995direct, vatani2009enhanced} so that the AM apparatus knows what to build for each layer.

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{../figures/literatureReview/literature_stl.png}
  \caption{An example of a CAD (left) converted to a STL file (right). Reprinted from \cite{gibson2010additive} with permission from Springer New York.}
  \label{fig:literature_stl}
\end{figure}

When the AM object is manufactured, post processing techniques can be done at this stage. For example sanding may be done to smooth the surfaces \citep{gibson2010additive}. The manufactured object may be inspected for pores or defects by comparing the x-ray image of the object with the CAD \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}.

@@

\subsection{Online Inspection and Defects}

The manufacturing process can be monitored, this is called online or in-situ process monitoring \citep{everton2016review}. The idea is that problems in the manufacturing are found as soon as possible before the final product is spoiled \citep{cerniglia2015inspection}.

There are various discontinuities in AM, in particular in the manufacturing of metal parts \citep{everton2016review}. For example gas can become trapped during the manufacturing process forming gas pores in the manufactured object \citep{thijs2010study, tammas2015xct}, they can be \SIrange{5}{20}{\micro\metre} in diameter \citep{everton2016review}. Layers may not fuse together and form elongated pores, this can be fixed by increasing the energy of the beam but too high will cause evaporation of the AM part \citep{mumtaz2008high}. They can be \SIrange{50}{500}{\micro\metre} in size \citep{everton2016review}. They are observable using a scanning electron microscope as shown in Figure \ref{fig:literature_pores}. Low wetting ability of the melt pool can cause balling, this is where the sintered powder has poor contact on the existing layer causing spherical particles to form on the surface of the AM part \citep{li2012balling, gu2009balling}. The spherical particles can vary in size of \SIrange{10}{500}{\micro\metre} \citep{li2012balling}. Low oxygen content in the environment \citep{niu1999instability} and higher energy beams \citep{gu2009balling} can reduce the balling effect. Some examples are shown in Figure \ref{fig:literature_balling} using an electron scanning microscope. Cracks can form due to extreme temperature changes and gradients \citep{mercelis2006residual, zaeh2010investigations}.

@@

Various methods are used for in-situ process monitoring. Most commonly a high speed camera is installed capturing the various wavelengths in the electromagnetic spectrum emitted by the melt pool \citep{berumen2010quality, craeghs2011online, lott2011design}. Various discontinuities and errors can be detected \citep{clijsters2014in} and be used to give feedback to the AM apparatus \citep{herzog2013method}. Other methods include measuring the surface using a laser \citep{cerniglia2015inspection} and using an infrared camera to measure the temperature of the melt pool \citep{rodriguez2012integration}.

@@

The setup of XCT \citep{cormack1973reconstruction, hounsfield1973computerized, hounsfield1980computed} in the medical field involves the patient laying on a bed. An x-ray source and x-ray detector pair rotate around and translate along the patient to get readings of the x-rays after attenuating the patient using different paths. X-ray beams were pencil beams in the early versions of XCT \citep{michael2001x}. To reduce scanning times, fan shaped beams and arrays of detectors were used and they can move in a spiral fashion along and around the patient \citep{cierniak2011x}. These multiple x-ray readings or images can be used to reconstruct a representation of the patient in 3D \citep{zeng2010medical}. This is illustrated in Figure \ref{fig:literature_medicalct}.

@@

Higher power x-rays can be used in XCT for the purpose of manufacturing and metrology because there is no consequence of the manufactured object being scanned absorbing the radiation. The XCT setup is different, the object is held by foam on a turntable and placed between an x-ray source and an x-ray detector. X-ray images are taken while the object rotates. Typically the x-ray is a cone beam \citep{kruth2011computed}. This is illustrated in Figure \ref{fig:literature_xct}.

@@

The electrons can interact with the anode in a number of ways. The electrons can be deflected or decelerated due to the electric field from the nucleus of the target anode material, the energy lost by the electrons is emitted as bremsstrahlung radiation. The energy of the bremsstrahlung radiation depends on the potential difference in the x-ray tube, as this determines the energy of the fired electrons, and also the proton number of the anode target because this affects the electric field produced by the nucleus in the anode target \citep{sun2012overview}. Another interaction is when the electrons may collide with the nucleus in the anode target, exciting an inner shell electron and ionizing it. This produce a vacancy in the electron shell and emits a photon when the excited electron drops down back to the ground state. This is known as characteristic radiation and the energy emitted is discrete and depends on the material in the anode target \citep{sun2012overview}.

@@

Photons, making up the radiation, are emitted from the x-ray tube as a Poisson process. The rate of x-ray emission depends on the current, that is the rate of charge between the cathode and anode. The energy of each photon are from bremsstrahlung radiation and characteristic radiation, making the distribution of x-ray photons energy a mix of continuous and discrete energies \citep{sun2012overview}. An example is shown in Figure \ref{fig:literature_spectrum}.

@@

The object being scanned are exposed to x-ray photons in XCT. X-ray photons undergo attenuation when interacting with the object in a number of ways \citep{cantatore2011introduction}. The object can absorb the photons via the photoelectric effect. In the photoelectric effect, the photons transfers all its energy to a bounded electron and ejects it from the object's atom \citep{millikan1916direct}. Photons can be scattered by the object by colliding inelastically with and transfers its energy to the an electron. This process is known as Compton scattering \citep{compton1923quantum}. The photoelectric effect and Compton scattering make a number of photons undetectable. However if some of the photons avoid these processes, they are detected and their energy is left unaffected.

@@

After attenuation, the x-ray photons are detected by the x-ray detector. The detectors used in XCT are typically flat bed scanners made up of a scintillator material \citep{curran1953luminescence, greskovich1997ceramic} and photodiodes. The x-ray photons interact with the scintiallator material and produce visible light \citep{rossner1993conversion}. The visible light is detected by photodiodes and coverts it into an electrical signal. The electrical signal can be a quantum counter, counting the number of photons detected, or an energy integrating detector, adding up all of the energies of each detected photon \citep{whiting2006properties, kruth2011computed}. The electrical signals are subject to sampling and quantisation to store these signals as an image \citep{cierniak2011x}.

Not all of the visible light photons are detected by the photodiodes, thus not all the x-ray photons are detected. The ratio between the number of x-ray photons detected by the detector and the number of x-ray photons arriving at the detector is called the quantum efficiency \citep{cierniak2011x}. The detection is a two stage process \citep{cierniak2011x}, although there exist equipment which detects x-ray directly such as a xenon gas ionization detector \citep{fuchs2000direct}, solid state CT systems such as sintillator-photodiodes detectors have high quantum efficiency of about 98\% to 99.5\% \citep{hsieh2000investigation}.

Once multiple x-ray images of the object have been acquired at multiple angles, the reconstruction process can start. The objective of reconstruction is to estimate the attenuation coefficient of the object at each point in space $\mu(x,y,z)$ using the x-ray images. It should be reminded that the x-ray images are based on the line integral of the attenuation coefficient along the path of photons. This problem was formed by \cite{radon1986on} as the `determination of functions from their integral values along certain manifolds'.

@@

XCT can be used to measure the length of the object, making it useful for measuring AM objects internally and externally. \emph{Nikon} offer products and services for XCT including features such as direct comparison to the CAD \citep{nikon2015microfocus, nikon2018mct225} and automated production line inspection \citep{nikon2015inline, nikon2018automated}.

@@

The set up of XCT has a number of variables. The potential difference and current of the x-ray tube can be adjusted to control the contrast and brightness of the x-ray image. The exposure time is also a factor. These settings should be set high enough to avoid beam extinction but low enough that there is contrast where less material is present \citep{kruth2011computed}. The magnification can be adjusted by adjusting the distances between the x-ray tube, the object and the x-ray detector. Increasing the magnification increases the image resolution but can cause blurry images, this is the result from using an x-ray source with a finite spot size as shown in Figure \ref{fig:literature_magnification} \citep{kruth2011computed}. Blurry results from larger spot sizes, this is know as the penumbra effect \citep{kueh2016modelling}. However, spot sizes too small can produce concentrated heat \citep{welkenhuyzen2009industrial} and can damage the x-ray tube.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{../figures/literatureReview/literature_angles.png}
  \caption{A reconstruction when scanning three aligned balls using a different number of angles. Reprinted from \cite{kruth2011computed} with permission from Elsevier.}
  \label{fig:literature_angles}
\end{figure}

@@

Problems can occur in the detector. For examples pixels in the acquired x-ray can be defected or dead \citep{brettschneider2014spatial} and the panel structure of the detector can appear \citep{yang2009evaluation}. Spatially correlated noise can be observed as well \citep{sun2016characterisation}.

@@

The most common use of XCT in AM is the investigation of pores in the manufactured object \citep{thompson2016x}. Pores can be classified as defects if the pores are larger than some volume threshold. This threshold controls the probability of the detection of defects \citep{gandossi2010probability, amrhein2014characterization}.

The porosity can be estimated by dividing the volume of all of the pores by the volume of solid material in the XCT scan \citep{taud2005porosity}. However more accurate methods of measuring the porosity can be done using Archimedes' method \citep{spierings2011comparison}. The strength of XCT comes from the fact that the location of the pores can be visualised, for example in Figure \ref{fig:literature_pores3D}, and compared to the CAD \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}. Studies have been done to link porosity to stress concentration \citep{leuders2015fatigue, siddique2015computed, carlton2016damage}. \cite{leuders2015fatigue} pointed out that the location of the pores is an important factor. In addition to pores, any surface deviation can be measured by aligning the reconstruction with the CAD and measuring any discrepancies \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}, an example is shown in Figure \ref{fig:literature_warnett}.

@@

\begin{figure}
  \centering
      \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/literatureReview/literature_warnett1.png}
      \caption{External}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/literatureReview/literature_warnett2.png}
      \caption{Internal}
    \end{subfigure}
    \caption{The reconstruction was aligned and compared to the CAD. The surface heat map shows the surface deviation (or `variance' in the literature) externally (a) and internally (b). Reprinted from \cite{warnett2016towards} under the CC BY 3.0 license.}
    \label{fig:literature_warnett}
\end{figure}

One of the disadvantages of XCT is that it is a slow process. Even in the marketing of \cite{nikon2015inline}'s inline quality control featured automatic reconstruction in the background with a progress bar. The reconstruction can take between 5 minutes to a number of hours \citep{warnett2016towards} however more images would improve the accuracy of the reconstruction \citep{kruth2011computed}. \cite{warnett2016towards} improved the speed of XCT by sacrificing accuracy of the reconstruction. This was done by placing the object to scan on a conveyor belt surrounded by multiple x-ray source and detector pairs as shown in Figure \ref{fig:literature_conveyor}. X-ray images at fewer angles can be taken but they can be obtained in one acquisition, speeding up the process.

@@

Instead of reconstructing the object, the analysis can be done on the x-ray images itself, or projection space, by comparing it to a simulation such as \emph{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}. \cite{brierley2018optimized} developed an algorithm to adjust the parameters of the simulation as well as aligning it so that it fits with the x-ray acquisition. It is however very complicated as it is optimising over a very large dimensional space. \cite{brierley2018optimized} also demonstrated that detection of defects is possible in projection space by comparing two simulations with each other, one with defects and the other without. It is however inevitable that accuracy is lost from the jump from 3D to 2D \citep{hayden2009chest}.

>>>>

X-ray computed tomography (XCT) can be used as a non-destructive test for AM products, this is the main theme of this thesis. Various reviews on AM exist such as \cite{kruth1991material, kruth1998progress, pham1998comparison, gibson2010additive, wong2012review, ngo2018additive}. For XCT used in manufacturing, there are \cite{cantatore2011introduction, kruth2011computed, sun2012overview}. \cite{thompson2016x} reviewed the applications of XCT on AM.

@@

Loosely, AM involves solidifying material onto a moving platform so that the object is manufactured layer by layer. Typically this is a slow and expensive method compared to destructive methods such as computer numerical control (CNC) machining for example. However, this is not the full picture. The set up cost for AM is low, in particular destructive methods requires planning and setting up various apparatus before the manufacturing stage \citep{gibson2010additive}. This is why AM used to be called rapid prototyping \citep{kruth1991material}, it was suitable to manufacture bespoke items.

@@

Fused deposition modelling is another liquid based AM technology. A jetting head, or nozzle, deposit the molten material onto a platform or on top of the previous layer. The material is usually plastic in a form of a thin filament. It is heated to just above its melting points, typically \SI{1}{\degreeCelsius} \citep{crump1992apparatus}, so that it cools down within \SI{0.1}{\second} \citep{kruth1991material}. The platform moves, and controlled by a computer, in the $x-y$ axis, or left to right and front to back, to produce a layer. The jetting head can move in the $z$ axis, or up and down, to manufacture the next layer. In the original patent by \cite{crump1992apparatus}, the thickness can be as thin as 0.000\,1 inches (\SI{0.003}{\milli\metre}).

@@

The blueprint of the object to be manufactured is called a computer-aided design (CAD) model. For it to be processed by an AM apparatus, the CAD model is converted to a STL file \citep{3d1989sterolithography, 3d2019what} which represent surfaces made up of a series of triangles, an example is shown in Figure \ref{fig:literature_stl}. STL stands for sterolithography but could also be called standard tessellation language \citep{wong2012review}. Some accuracy is lost here as the surface of the CAD model is represented approximately by triangles \citep{gibson2010additive}. The STL file is then sliced into layers \citep{jamieson1995direct, vatani2009enhanced} so that the AM apparatus knows what to build for each layer.

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{../figures/literatureReview/literature_stl.png}
  \caption{An example of a CAD model (left) converted to a STL file (right). Reprinted from \cite{gibson2010additive} with permission from Springer New York.}
  \label{fig:literature_stl}
\end{figure}

When the AM object is manufactured, post processing techniques can be done at this stage. For example sanding may be done to smooth the surfaces \citep{gibson2010additive}. The manufactured object may be inspected for pores or defects by comparing the x-ray image of the object with the CAD model \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}.

@@

\subsection{Defects and Quality Control}

There are various discontinuities in AM. In FDM, a staircase effect on the surface of the product arises from poor slicing methods of the CAD model \citep{weeren1995quality}. Internal voids can be formed due to insufficient material flow \citep{weeren1995quality}. Other factors which can cause defects include misalignment of the platform or nozzle, depletion of material and lack of adhesion due to low temperatures \citep{gunaydin2018common}. There are also problems in the manufacturing of metal parts \citep{everton2016review}. For example gas can become trapped during the manufacturing process forming gas pores in the manufactured object \citep{thijs2010study, tammas2015xct}, they can be \SIrange{5}{20}{\micro\metre} in diameter \citep{everton2016review}. Layers may not fuse together and form elongated pores, this can be fixed by increasing the energy of the beam but too high will cause evaporation of the AM part \citep{mumtaz2008high}. They can be \SIrange{50}{500}{\micro\metre} in size \citep{everton2016review}. They are observable using a scanning electron microscope as shown in Figure \ref{fig:literature_pores}. Low wetting ability of the melt pool can cause balling, this is where the sintered powder has poor contact on the existing layer causing spherical particles to form on the surface of the AM part \citep{li2012balling, gu2009balling}. The spherical particles can vary in size of \SIrange{10}{500}{\micro\metre} \citep{li2012balling}. Low oxygen content in the environment \citep{niu1999instability} and higher energy beams \citep{gu2009balling} can reduce the balling effect. Some examples are shown in Figure \ref{fig:literature_balling} using an electron scanning microscope. Cracks can form due to extreme temperature changes and gradients \citep{mercelis2006residual, zaeh2010investigations}.

@@

The manufacturing process can be monitored, this is called online or in-situ process monitoring \citep{everton2016review}. The idea is that problems in the manufacturing are found as soon as possible before the final product is spoiled \citep{cerniglia2015inspection}. Various methods are used for in-situ process monitoring. Most commonly a high speed camera is installed capturing the various wavelengths in the electromagnetic spectrum emitted by the melt pool \citep{berumen2010quality, craeghs2011online, lott2011design}. Various discontinuities and errors can be detected \citep{clijsters2014in} and be used to give feedback to the AM apparatus \citep{herzog2013method}. Other methods include measuring the surface using a laser \citep{cerniglia2015inspection} and using an infrared camera to measure the temperature of the melt pool \citep{rodriguez2012integration}.

@@

The setup of XCT \citep{cormack1973reconstruction, hounsfield1973computerized, hounsfield1980computed} in the medical field involves the patient laying on a bed. An x-ray source and x-ray detector pair rotate around and translate along the patient to get readings of the x-rays after attenuating through the patient using different paths. X-ray beams were pencil beams in the early versions of XCT \citep{michael2001x}. To reduce scanning times, fan shaped beams and arrays of detectors were used and they can move in a spiral fashion along and around the patient \citep{cierniak2011x}. These multiple x-ray readings can be used to reconstruct a representation of the patient in 3D \citep{zeng2010medical}. This is illustrated in Figure \ref{fig:literature_medicalct}.

@@

High power x-rays can be used in XCT for the purpose of manufacturing and metrology because there is no consequence of the manufactured object absorbing the radiation. The XCT setup is different, the object is held by foam on a turntable and placed between an x-ray source and an x-ray detector. X-ray projections are taken while the object rotates. Typically the x-ray is a cone beam \citep{kruth2011computed}. This is illustrated in Figure \ref{fig:literature_xct}.

@@

The electrons can interact with the anode in a number of ways. The electrons can be deflected or decelerated due to the electric field from the nucleus of the target anode material. The energy lost by the electrons is emitted as bremsstrahlung radiation. It depends on the potential difference in the x-ray tube, as this determines the energy of the fired electrons, and also the proton number of the anode target because this affects the electric field produced by the nucleus in the anode target \citep{sun2012overview}. Another interaction is when the electrons may collide with the nucleus in the anode target, exciting an inner shell electron and ionizing it. This produce a vacancy in the electron shell and emits a photon when the excited electron drops down back to the ground state. This is known as characteristic radiation and the energy emitted is discrete and depends on the material in the anode target \citep{sun2012overview}.

@@

Photons, making up the radiation, are emitted from the x-ray tube as a Poisson process \citep{cierniak2011x}. The rate of x-ray emission depends on the current, that is the rate of charge between the cathode and anode. The energy of each photon are from bremsstrahlung radiation and characteristic radiation, making the distribution of x-ray photons energy a mix of continuous and discrete energies \citep{sun2012overview}. An example is shown in Figure \ref{fig:literature_spectrum}.

@@

The scanned object are exposed to x-ray photons which undergoes attenuation when interacting with the object in a number of ways \citep{cantatore2011introduction}. The object can absorb the photons via the photoelectric effect. In the photoelectric effect, the photons transfers all its energy to a bounded electron and ejects it from the object's atom \citep{millikan1916direct}. Photons can be scattered by the object by colliding inelastically with and transfers its energy to an electron. This process is known as Compton scattering \citep{compton1923quantum}. The photoelectric effect and Compton scattering make a number of photons undetectable. However if some of the photons avoid these processes, they are detected and their energy is left unaffected.

@@

After attenuation, the x-ray photons are detected by the x-ray detector. The detectors used in XCT are typically flat bed scanners made up of a scintillator material \citep{curran1953luminescence, greskovich1997ceramic} and photodiodes. The x-ray photons interact with the scintiallator material and produce visible light pluses \citep{rossner1993conversion}. These pulses are detected by photodiodes and converted into an electrical signal \citep{nikl2006scintillation, ren2018tutorial}. The electrical signal can be a quantum counter, counting the number of photons detected, or an energy integrating detector, adding up all of the energies of each detected photon \citep{nikl2006scintillation, whiting2006properties, kruth2011computed, ren2018tutorial}. The electrical signals are subject to sampling and quantisation to store these signals as an image \citep{cierniak2011x}. This image is known as a projection.

Not all of the visible light pulses are detected by the photodiodes, thus not all the x-ray photons are detected. The ratio between the number of x-ray photons detected by the detector and the number of x-ray photons arriving at the detector is called the quantum efficiency \citep{cierniak2011x, ren2018tutorial}. The detection is a two stage process \citep{cierniak2011x}, although there exist equipment which detects x-ray directly such as a xenon gas ionization detector \citep{fuchs2000direct}, solid state CT systems such as sintillator-photodiodes detectors have high quantum efficiency of about 98\% to 99.5\% \citep{hsieh2000investigation}.

Once multiple projections of the object have been acquired at multiple angles, the reconstruction process can start. The objective of reconstruction is to estimate the attenuation coefficient of the object at each point in space $\mu(x,y,z)$ using the x-ray projections. This is done using the fact that the projections are based on the line integral of the attenuation coefficient along the path of photons. This problem was formed by \cite{radon1986on} as the `determination of functions from their integral values along certain manifolds'.

@@

XCT can be used to measure the length of the object, making it useful for measuring AM objects internally and externally. \emph{Nikon} offer products and services for XCT including features such as direct comparison to the CAD model \citep{nikon2015microfocus, nikon2018mct225} and automated production line inspection \citep{nikon2015inline, nikon2018automated}.

@@

The set up of XCT has a number of variables. The potential difference and current of the x-ray tube can be adjusted to control the contrast and brightness of the x-ray projection. The exposure time is also a factor. These settings should be set high enough to avoid beam extinction but low enough that there is contrast where less material is present \citep{kruth2011computed}. The magnification can be adjusted by adjusting the distances between the x-ray tube, the object and the x-ray detector. Increasing the magnification increases the image resolution but can cause blurry images, this is the result from using an x-ray source with a finite spot size as shown in Figure \ref{fig:literature_magnification} \citep{kruth2011computed}. Larger spot sizes cause more blurry results, this is known as the penumbra effect \citep{kueh2016modelling}. However, spot sizes too small can produce concentrated heat \citep{welkenhuyzen2009industrial} and can damage the x-ray tube.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{../figures/literatureReview/literature_angles.png}
  \caption{A reconstruction when scanning three aligned balls using a different number angular projections. Reprinted from \cite{kruth2011computed} with permission from Elsevier.}
  \label{fig:literature_angles}
\end{figure}

@@

Problems can occur in the detector. For examples pixels in the acquired projection can be defected or dead \citep{brettschneider2014spatial} and the panel structure of the detector can be observed \citep{yang2009evaluation}. Spatially correlated noise within a projection can be observed \citep{sun2016characterisation} as well as correlation between acquisitions, this is known as image lag \citep{yang2009evaluation}. Precautions can be taken reduce the impact from image lag such as waiting for 20 minutes between acquisitions \citep{yang2010noise}.

@@

The most common use of XCT in AM is the investigation of pores in the manufactured object \citep{thompson2016x}. Pores can be classified as defects if the pores are larger than some volume threshold. This threshold controls the probability of the detection of defects \citep{gandossi2010probability, amrhein2014characterization}. The porosity can be estimated by dividing the volume of all of the pores by the volume of solid material in the XCT scan \citep{taud2005porosity}. Accurate methods of measuring the porosity can be done using Archimedes' method \citep{spierings2011comparison}.

An advantage of XCT is that the location of the pores can be visualised, for example in Figure \ref{fig:literature_pores3D}, and compared to the CAD model \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}. Studies have been done to link porosity to stress concentration \citep{leuders2015fatigue, siddique2015computed, carlton2016damage}. The location of the pores is a good predictor of fatigue strength \citep{leuders2015fatigue}. In addition to pores, any surface deviation can be measured by aligning the reconstruction with the CAD model and measuring any discrepancies \citep{lee2015compliance, villarraga2015assessing, kim2016inspection}, an example is shown in Figure \ref{fig:literature_warnett}.

@@

\begin{figure}
  \centering
      \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/literatureReview/literature_warnett1.png}
      \caption{External}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
      \includegraphics[width=\textwidth]{../figures/literatureReview/literature_warnett2.png}
      \caption{Internal}
    \end{subfigure}
    \caption{The reconstruction was aligned and compared to the CAD model. The surface heat map shows the surface deviation (or `variance' in the literature) externally (a) and internally (b). Reprinted from \cite{warnett2016towards} under the CC BY 3.0 license.}
    \label{fig:literature_warnett}
\end{figure}

One of the disadvantages of XCT is that it is a slow process. XCT is not an instantaneous process so progress bars are usually featured in XCT marketing such as \cite{nikon2015inline}'s inline quality control. The reconstruction can take between 5 minutes to a number of hours \citep{warnett2016towards} however more images would improve the accuracy of the reconstruction \citep{kruth2011computed}. \cite{warnett2016towards} improved the speed of XCT by sacrificing accuracy of the reconstruction. This was done by placing the object to scan on a conveyor belt surrounded by multiple x-ray source and detector pairs as shown in Figure \ref{fig:literature_conveyor}. Fewer angular projections were taken but they can be obtained in one go, speeding up the process.

@@

Instead of reconstructing the object, the analysis can be done on the projections itself, or in projection space, by comparing it to a simulated projection produced by software called \emph{aRTist} \citep{bellon2007artist, jaenisch2008artist, bellon2012radiographic}. \cite{brierley2018optimized} developed an algorithm to adjust the parameters of the simulation as well as aligning it so that it fits with the x-ray acquisition. It is however very complicated as it is optimising over a very large dimensional space. \cite{brierley2018optimized} also demonstrated that detection of defects is possible in projection space by comparing two simulated projections with each other, one with defects and the other without. Another method is to use machine learning methods to classify defects from a projection \citep{rale2009comparison}.

It is however inevitable that accuracy is lost from the jump from reconstruction space to projection space, for example, a CT scan has superior performance in the diagnostic of pneumonia compared to a chest radiograph \citep{hayden2009chest}.
